\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-05-14 doc/sw-system.tex
Corrected offline downweighting sentence to mention Laplace/add-one smoothing #210

We refer to this alternative calculation as ``offline'' analysis, because it
does not need to be carried out one classification at a time (and hence can be
done at any time after the data is collected). Note that in this offline
inference, the effect will be that of applying the time-averaged confusion
matrices to each classification,  rather than a set that evolves as the agents
(and in the real world, the volunteers) learn. This will mean  that the early
classifications will effectively not be downweighted as a result of the agent's
ignorance. On the other hand, this ignorance provides some conservatism,
reducing the noise due to early classifications if they are unreliable: in
practice we ignore the first two classifications made by  each volunteer, for
this reason. Whether or not an offline analysis out-performs an online one is a
matter for experiment.

>>>>

We refer to this alternative calculation as ``offline'' analysis, because it
does not need to be carried out one classification at a time (and hence can be
done at any time after the data is collected). Note that in this offline
inference, the effect will be that of applying the time-averaged confusion
matrices to each classification,  rather than a set that evolves as the agents
(and in the real world, the volunteers) learn. This will mean  that the early
classifications will effectively not be downweighted as a result of the agent's
ignorance. On the other hand, this ignorance provides some conservatism,
reducing the noise due to early classifications if they are unreliable: in
practice we do downweight (via Laplace/add-one smoothing)
the early classifications made by each volunteer, for
this reason. Whether or not an offline analysis out-performs an online one is a
matter for experiment.
